---
title: "YKunwar_LiveSession4Assignment"
author: "Yejur Kunwar"
date: "9/26/2017"
output: 
html_document: 
 assignment4_md : TRUE
 
---
# Live session Unit 04 assignment

# Questions

##1. FiveThirtyEight Data
#####a. Installing the fivethirtyeight package
install.packages("fivethirtyeight")
```{r, echo = TRUE}
setwd("~/MSDS6306/Test_git")
library(fivethirtyeight)
```
#####b. Assigning eighteenth data set to an object df
```{r, echo = TRUE}
data(package= "fivethirtyeight")
df<- fivethirtyeight::college_recent_grads
```
#####c. Detailed list of the datasets to write out the URL in a comment to the related news story
* The eighteenth data set assigned above can be found in fivethrieight package installed in R by assigning command below. The URL to reach the datasets in github is https://github.com/rudeboybert/fivethirtyeight/blob/master/README.md. 
* The actual URL for eighteenth data set in fivethirtyeight package can be reached via http://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/.
```{r, echo = TRUE}
# More detailed list of data set can be displayed by this command below.
vignette("fivethirtyeight", package = "fivethirtyeight")
```
#####d. Dimensions and columns of this dataframe
```{r, echo = TRUE}
dim(df) # Dimensions of df
colnames(df) # Column names in df
```
#2. Data Summary
#####a. Column names of data frame and count the number of columns
```{r, echo = TRUE}
colnames(df) # Column names in df
ncol(df) # Number of Column in df
```
#####b. Generating a count of each major_category and assigning to major_count
```{r, echo = TRUE}
# Count of each unique major_category in the data frame and assigning column names in an object major_count
major_count <- as.data.frame(table(df$major_category)) 
colnames(major_count) <- c("Majors", "Frequency")
major_count
```
#####c. Barplot for major_count
```{r, echo = TRUE}
par(las = 2)
barplot(major_count$Frequency, names = major_count$Majors, horiz = TRUE, main = "Frequency of College Majors", xlab = "Frequency", ylab = "", col = "blue")

```  

#####d. Writing fivethirtyeight data to a csv file, no row labels
```{r, echo = TRUE}
write.csv(df, file='eighteenth_fivethirtyeight.csv', row.names = FALSE)

write.csv(major_count, file = 'freq_majors.csv', row.names = FALSE )
```
#3. Codebook
Please follow the link to go to gihub codebook:
* Link: https://github.com/yejurkunwar/SMU-MSDS-homework


# Displaying sessionInfo for documentation
```{r, echo = TRUE}
sessionInfo()
```
